%!TEX root = ./main.tex
\section*{Machine Learning Problem}
As training data we store a lot of played games from the perspective of the winner (for example from very good players). 

We choose as features: which cards we (the winning player) get at the beginning, cards that are revealed by the dealer and the amount of money all players put into the pot. The label is the amount of money we should bet (0 for passing, -1 for fold).

Given all the features we want to know from our system how much money we should bet in each round. For the learning step we need to learn or train a function/distribution which tells us how much money to bet. This supervised learning problem can be solve with a nearest neighbour classifier (in the simplest case). For the evaluation of our system we could compete in online poker games and win a lot of money. A more elaborate learning system could try to find a model for the behaviour of the opponents and use this as an additional feature for our learner. 



\section*{Probability Theory}

\begin{eqnarray} 
    p(x|z)p(y|x,z) &=&  \frac{p(x,z)}{p(z)}\cdot \frac{p(x,y,z)}{p(x,z)} \\
    &=&  \frac{p(x,y,z)}{p(z)} \\
    &=&  p(x,y|z) 
\end{eqnarray}

\begin{eqnarray}
    \frac{p(y| x,z)p(x|z)}{p(y|z)}&=& \frac{\frac{p(x,y,z)}{p(x,z)} \frac{p(x,z)}{p(z)}}{\frac{p(y,z)}{p(z)}} \\
    &=& \frac{p(x,y,z)}{p(y,z)} \\
    &=& p(x|y,z) 
\end{eqnarray}


\begin{eqnarray}
    \mathbb{E}[X]+\mathbb{E}[Y]&=& \sum_{X}(x_i p(x_i)) + \sum_{Y}(y_i p(y_i))\\
    &=& \sum_{X, Y}(x_i p(x_i)p(y_i)) + \sum_{X,Y}(y_i p(x_i)p(y_i))\\
    &=& \sum_{X, Y}(x_i p(x_i,y_i)) + \sum_{X,Y}(y_i p(x_i,y_i)) \hspace{4mm}\mbox{because of independence}\\
    &=& \sum_{X, Y}((x_i+y_i) p(x_i,y_i))\hspace{1cm}\\
    &=& \mathbb{E}[X+Y]
\end{eqnarray}

\begin{eqnarray}
    \text{var}[X+Y]&=& \mathbb{E}[(X+Y)^2] - [\mathbb{E}[X+Y]]^2\\
    &=& \mathbb{E}[X^2+2XY+Y^2] - [\mathbb{E}[X]+\mathbb{E}[Y]]^2 \hspace{5mm}\mbox{using (3)}\\
    &=& \mathbb{E}[X^2]+\mathbb{E}[2XY]+\mathbb{E}[Y^2] - [\mathbb{E}[X]+\mathbb{E}[Y]]^2 \hspace{5mm}\mbox{using (3)}\\
    &=& \mathbb{E}[X^2]+\mathbb{E}[2XY]+\mathbb{E}[Y^2] - \mathbb{E}[X]^2-2[\mathbb{E}[X]\mathbb{E}[Y]] -\mathbb{E}[Y]^2 \\
    &=& \mathbb{E}[X^2]- \mathbb{E}[X]^2 +\mathbb{E}[Y^2]-\mathbb{E}[Y]^2 -2[\mathbb{E}[X]\mathbb{E}[Y]] +\mathbb{E}[2XY]  \\
    &=& \text{var}[X] +\text{var}[Y] -2[\mathbb{E}[X]\mathbb{E}[Y]] +\mathbb{E}[XY]]  \\
    &=& \text{var}[X] +\text{var}[Y] -2[\text{covar}[X,Y]]  \\
    &=& \text{var}[X] +\text{var}[Y]\hspace{5mm}\mbox{since X,Y are uncorrelated} 
\end{eqnarray}
